Fractional Decomposition Tree Algorithm: A tool for studying the integrality gap of Integer Programs

### 2020-06-12 FDT2020/Introduction.tex
quick edit

% A common approach to Integer programming is considering their linear relaxation.
For some problems such as the \textsc{Minimum Cost Spanning Tree Problem} there are linear programming relaxations whose basic feasible solutions coincide with  integral solutions, i.e. spanning trees.

@@

A polynomial time algorithm for proving an upper bound on integrality gap is called an LP-based approximation algorithm. For many well studied problems, we still do not know the exact integrality gap and the gap between the best known lower bound and the upper bound on the integrality gap are open. In some cases, there are known upper bounds, yet there is no known approximation algorithm, meaning that the proofs do not yield polynomial time algorithms.
}\fi 
The set of feasible points for a pure IP (henceforth IP) is the set
\begin{equation}
S(A,b)= \{x\in \mathbb{Z}^{n}\;:\; Ax\geq b\}  \label{S}.
\end{equation}
If we drop the integrality constraints, we have the linear relaxation of set $S(A,b)$,
\begin{equation}
P(A,b) = \{x\in \mathbb{R}^{n}\;:\; Ax\geq b\}. \label{P}
\end{equation}
Let $I=(A,b)$ denote an instance. Then $S(I)$ and $P(I)$ denote $S(A,b)$ and $P(A,b)$, respectively. Given a linear objective function $c$, an IP is $\min \;\{cx:\; x \in S(I)\}$.

>>>>

% A common approach to Integer programming is considering their linear relaxation.
\cindy{TODO: this has to move to a logical place, problem in the more formal treatment below.}
For some problems such as the \textsc{Minimum Cost Spanning Tree Problem} there are linear programming relaxations whose basic feasible solutions coincide with  integral solutions, i.e. spanning trees.

@@

A polynomial time algorithm for proving an upper bound on integrality gap is called an LP-based approximation algorithm. For many well studied problems, we still do not know the exact integrality gap and the gap between the best known lower bound and the upper bound on the integrality gap are open. In some cases, there are known upper bounds, yet there is no known approximation algorithm, meaning that the proofs do not yield polynomial time algorithms.
}\fi 
We now describe IPs and our methods more formally. The set of feasible points for a pure IP (henceforth IP) is the set
\begin{equation}
S(A,b)= \{x\in \mathbb{Z}^{n}\;:\; Ax\geq b\}  \label{S}.
\end{equation}
If we drop the integrality constraints, we have the linear relaxation of set $S(A,b)$,
\begin{equation}
P(A,b) = \{x\in \mathbb{R}^{n}\;:\; Ax\geq b\}. \label{P}
\end{equation}
Let $I=(A,b)$ denote an instance. Then $S(I)$ and $P(I)$ denote $S(A,b)$ and $P(A,b)$, respectively. Given a linear objective function $c$, an IP is $\min \;\{cx:\; x \in S(I)\}$.
